The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-24 paper/sections/methods.tex
some more words, free of charge

\subsection{Choosing Deformation Centers}
\label{sec:origins}
\dave{Ty: try to follow this formula when writing 
\dave{maybe this should come after weight computation ?}
(1) what is the purpose of this part of the method ?
(2) what are the criteria for success
(3) what is our assumed input 
(4) what is the desired output
(5) what's the algorith,
(6) add proofs/diagrams/figures that show we satisfy (2). }
To ensure kinematic expressiveness, it is essential that multiple origins of deformation are permitted. Each part, $\prt_i$, must be associated with a single deformation origin, $\bar{\refX}_j$. Each origin is computed as the centroid of the set of parts with which it is associated. While we constraint a part to be paired with only one origin, an origin may be associated any number of parts. Next, we require that each deformation origin be associated with a minimum of two part so that we avoid having an origin lie on the surface of a part.\ty{Should we mention periodic surfaces? You can have a periodic nurbs sphere consisting of a single surface, which we couldn't handle with this constraint (easy fix, but not sure if worth mentioning)} Furthermore, we seek that the sparsity of the deformation origins mirrors that of the blending weights. Intuitively, this means that regions in which the weights are high for a subset of parts should deform about an origin centered in this region.

\begin{figure}[h]
    \includegraphics[width=\columnwidth]{figures/origin_network}
    \caption{Example structure for the network flow selection of deformation origins with an example shape on the right. Red arrows indicate each parts origin association.}
    \label{fig:multiparts}
\end{figure}

From the set of blending weights we seek to construct a set of candidate deformation origins and then produce a set of deformation origins, $\XBs$, adhering to the outlined requirements. These requirements admit a graph structure ~(\reffig{multiparts}), which we exploit by forming a simple network flow problem that produces a solution satisfying the requirements. The pairwise relationships between parts and deformation origins can be realized as a bipartite network flow problem. Flow between a part and origin is constrained to binary values and a flow value on edge between a part and origin candidate indicate that the part is paired with this deformation origin. We organize the problem so that the source node is connected to each candidate origin node, and the sink node is connected with each part. We place a capacity constraint of $1$ on the sink's edge, which enforces the constraint that each part is paired with one origin.

>>>>

\subsection{Choosing Deformation Centers}
\label{sec:origins}
\dave{Ty: try to follow this formula when writing 
\dave{maybe this should come after weight computation ?}
(1) what is the purpose of this part of the method ?
(2) what are the criteria for success
(3) what is our assumed input 
(4) what is the desired output
(5) what's the algorith,
(6) add proofs/diagrams/figures that show we satisfy (2). }
To ensure kinematic expressiveness, it is essential that multiple origins of deformation are permitted. Each part, $\prt_i$, must be associated with a single deformation origin, $\bar{\refX}_j$. Each origin is computed as the centroid of the set of parts with which it is associated. While we constraint a part to be paired with only one origin, an origin may be associated any number of parts. Next, we require that each deformation origin be associated with a minimum of two part so that we avoid having an origin lie on the surface of a part.\ty{Should we mention periodic surfaces? You can have a periodic nurbs sphere consisting of a single surface, which we couldn't handle with this constraint (easy fix, but not sure if worth mentioning)} Furthermore, we seek that the sparsity of the deformation origins mirrors that of the blending weights. Intuitively, this means that for a region in which weights are high for a subset of parts, the origin of deformation should be centered in this region.

\begin{figure}[h]
    \includegraphics[width=\columnwidth]{figures/origin_network}
    \caption{Example structure for the network flow selection of deformation origins with a shape consisting of three parts. Red arrows indicate each parts origin association.}
    \label{fig:multiparts}
\end{figure}

From the set of blending weights we seek to construct a set of candidate deformation origins and then produce a set of deformation origins, $\XBs$, adhering to the outlined requirements. These requirements admit a graph structure ~(\reffig{multiparts}), which we exploit by forming a simple network flow problem that produces a solution satisfying the requirements. The relationships between parts and deformation origins can be realized as a bipartite min-cost-flow problem.

Consider a directed bipartite graph $G=(V = A \cup B,E)$ where each node in $A$ corresponds to a deformation origin candidate and each node in $B$ represents one part. $E$ is the set of edges connecting nodes in $A$ to $B$ where each origin has an each to every part with which it attempts to associate. We augment $G$ to form $G'=(V' = A \cup B \cup \{s,t\}, E')$ where $V'$  is the new set of nodes now containing the source, $s$, and sink, $t$, nodes. $E'$ is the augmented set of nodes connecting $s$ to each candidate in $A$ and connecting each part in $B$ to the sink $t$. Each edge $(i,j) \in E'$ has an associated flow $f_{ij}$ and capacity constraint $u_{ij}$, and each edge in $E'$ also has a cost $c_{ij}$. The principal constraint for this network flow problem is the conservation constraint, meaning that the net flow for all nodes in $V$ is zero.

First, we constrain all flow values to be integral and place a capacity of $1$ on the edges from $B$ to $t$. This has the effect of enforcing that any node in $B$ receives flow from a single edge, and as a consequence each part may only be associated with a single deformation origin. 
Flow between a part and origin is constrained to binary values and a flow value on edge between a part and origin candidate indicate that the part is paired with this deformation origin. We organize the problem so that the source node is connected to each candidate origin node, and the sink node is connected with each part. We place a capacity constraint of $1$ on the sink's edge, which enforces the constraint that each part is paired with one origin.
